The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-12-06 papers/pair-correlation/paper.tex
add 1/r^6 potential to pairs paper (and update some MC data) Tested on collins. Took 1:29.90.
clean up da1dz text a bit, and use higher resolution in plots Tested on collins. Took 2:19.60.

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.}\label{fig:dadz}
\end{figure}

@@

We plot in Fig.~\ref{fig:dadz} this quantity for two pair potentials
near a hard wall.  Figure~\ref{fig:dadz-delta} shows the results for a
delta-function interaction at contact, which represents a so-called
``sticky hard-sphere fluid.''  Our pair distribution function is
constructed to produce this result exactly, provided the averaged pair
distribution function at contact from Ref.~\citenum{schulte2012using}
is exact.  As expected, we see excellent agreement with the Monte
Carlo simulation results, while the approximations of Fischer and
Sokolowski each show deviations near the interface.
Figure~\ref{fig:dadz-square-well} shows the same curve from
Eq.~\ref{eq:da1} for a square-well fluid.  We have chosen a square
well fluid with a potential range of 1.79, which is the optimal value
found for a SAFT-based model of water~\cite{clark2006developing}.
This potential stresses our approximation to the radial distribution
function, which results in less satisfactory results near a
hard-sphere diameter from the wall.  We see that over these length
scales, Sokolowski's approximation is very accurate.

>>>>

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.}\label{fig:dadz}
\end{figure}

@@

We plot in Fig.~\ref{fig:dadz} this quantity for hard-core fluids with
three representative pair potentials near a hard wall.  We have chosen
to illustrate a delta-function ineraction at contact (i.e. ``sticky
hard spheres''), a hard-core square-well fluid, with the length-scale
of interaction taken from the optimal SAFT model for water found by
Clark \emph{et al.}~\cite{clark2006developing}, and a $1/r^6$
power-law attraction.  These pair potentials represent a short-range
interaction, a medium-range discontinuous interaction, and a
long-range smooth interaction.

Figure~\ref{fig:dadz-delta} shows the results for the sticky
hard-sphere fluid.  Our pair distribution function is constructed to
produce this result exactly, provided the averaged pair distribution
function at contact from Ref.~\citenum{schulte2012using} is exact.  As
expected, we see excellent agreement with the Monte Carlo simulation
results, while the approximations of Fischer and Sokolowski each show
deviations near the interface.  Figure~\ref{fig:dadz-square-well}
shows the same curve from Eq.~\ref{eq:da1} for the square-well fluid.
This potential stresses our approximation to the radial distribution
function, since the edge of the attraction occurs at the dip in the
radial distribution function at this density, which poor results for
the bulk fluid.  We see that over these length scales, Sokolowski's
approximation is very accurate.  Finally, in the case of the power-law
attraction both approximations work very well.
